Connecting the Popularity Adjusted Block Model to the Generalized Random Dot Product Graph

### 2020-07-11 pabm-notes.Rmd
uploading scratch file to resume work on server

---
title: "Connecting the Popularity Adjusted Block Model to the Generalized Random Dot Product Graph"
output: pdf_document
# output: html_document
# geometry: "left=1cm,right=1cm,top=1cm,bottom=1.5cm"
urlcolor: blue
header-includes:
- \usepackage{float}
- \usepackage{mathtools}
---

@@

  Z.candidate <- Z.hat %*% R
  B <- Z.candidate %*% t(Z.candidate)
  return(sum(apply(Z.candidate[, 1:2] ** 2, 1, min)) + 
           sum(apply(cbind((Z.candidate[, 3] - Z.candidate[, 4]) ** 2,
                           (Z.candidate[, 3] + Z.candidate[, 4]) ** 2), 
                     1, min)))
}

transform.embedding <- function(Z.hat) {
  init.angles <- runif(4, -pi, pi)
  angles.1 <- optim(init.angles, function(x) obj.fun(x, Z.hat), 
                    method = 'SANN')$par
  angles.2 <- optim(angles.1, function(x) obj.fun(x, Z.hat),
                    method = 'Nelder-Mead',
                    control = list(abstol = 1e-10, maxit = 1e6))$par
  R <- construct.Q(angles.2)
  return(Z.hat %*% R)
}
```

@@

$S_3(-\tau) = \begin{bmatrix}
\cosh \tau & 0 & 0 & \sinh(-\tau) \\
0 & 1 & 0 & 0 \\
0 & 0 & 1 & 0 \\
\sinh(-\tau) & 0 & 0 & \cosh \tau
\end{bmatrix}$

>>>>

---
title: "Connecting the Popularity Adjusted Block Model to the Generalized Random Dot Product Graph"
# output: pdf_document
output: html_document
# geometry: "left=1cm,right=1cm,top=1cm,bottom=1.5cm"
urlcolor: blue
header-includes:
- \usepackage{float}
- \usepackage{mathtools}
---

@@

  XU.c <- Z.hat %*% R
  # clusters <- apply(XU.c[, 1:2] ** 2, 1, which.min)
  clusters <- c(rep(1, 32), rep(2, 32))
  in.prods <- XU.c[clusters == 1, ] %*% t(XU.c[clusters == 2, , drop = FALSE])
  return(
    sum(apply(XU.c[, 1:2] ** 2, 1, min)) +
      sum(apply(cbind((XU.c[, 3] - XU.c[, 4]) ** 2,
                      (XU.c[, 3] + XU.c[, 4]) ** 2),
                1, min))
    )
  # return(
  #   sum(apply(XU.c[, 1:2] ** 2, 1, min)) +
  #     Matrix::norm(in.prods, 'F') +
  #     sum((XU.c[clusters == 1, 3] - XU.c[clusters == 1, 4]) ** 2) +
  #     sum((XU.c[clusters == 2, 3] + XU.c[clusters == 2, 4]) ** 2)
  # )
}

transform.embedding <- function(Z.hat) {
  init.angles <- runif(4, -pi, pi)
  angles.1 <- optim(init.angles, function(x) obj.fun(x, Z.hat), 
                    method = 'SANN')$par
  angles.2 <- optim(angles.1, function(x) obj.fun(x, Z.hat),
                    method = 'Nelder-Mead',
                    control = list(abstol = 1e-10, maxit = 1e3))$par
  R <- construct.Q(angles.2)
  return(Z.hat %*% R)
}
```

@@

$S_3(-\tau) = \begin{bmatrix}
\cosh \tau & 0 & 0 & -\sinh \tau \\
0 & 1 & 0 & 0 \\
0 & 0 & 1 & 0 \\
-\sinh \tau & 0 & 0 & \cosh \tau
\end{bmatrix}$
